Comb associative operads

### 2018-09-03 CAs_operads.tex
Quelques corrections d'anglais

However, this completion algorithm depends on the other we choose. 
We might found a finite presentation using a different order.

\Todo{Expliquer algo et résultats}

>>>>

However, this completion algorithm depends on the order we choose.
In order to find out if the completion algorithm leads to a finite 
convergent presentation using a different order, we run the following
algorithm.

For every branching pair $(\Tfr_1, \Tfr_2)$ which is not joinable,
we recursively try to find a completion of $\Rew$ with
the new rule $\Tfr_1 \Rew  \Tfr_2$ and with the new rule 
$\Tfr_2 \Rew  \Tfr_1$. If at any moment the rewrite relation induced by
$\Rew$ loops then we simply reject it.

\Todo{résultats}
